Model Checking Differentially Private Properties

### 2018-01-26 applications.tex
motivate pan privacy

In stream
processing mechanisms, input data are retrieved and analyzed
continuously.

Continual observation is commonly found in on-line service
providers~\cite{DNPR:10:DPCO,DNPRY:10:PPSA}. 
Consider monitoring events $a$ and $b$ by streaming inputs. We would
like to compute the number of event types occurred in inputs.

>>>>

Streaming processing gives another motivating example for Markov
decision processes. In stream processing, input data are retrieved and
analyzed continuously. Such continual observation is commonly found
in social media, service providers, or even electronic surveillance
systems. To protect privacy, differentially private mechanisms have
been formulated and designed~\cite{DNPR:10:DPCO,DNPRY:10:PPSA}. 
We model a discrete variant of the mechanisms by Markov decision processes.

For illustration, consider monitoring events of the types $a$ and $b$
continuously. An observation is a sequence of event types. We would
like to compute the number of event types in observations. Hence for
observations $a \cdots a$ and $b \cdots b$ of arbitrary positive
lengths, the query result is $1$; and the query result is $2$ for
other non-empty observations.

In order to formulate differential privacy, define two obsevations
are \emph{neighbors} if one can be obtained from the other by replacing
event types any number of times, that is, if they are of the same
length. \bw{Later, we will consider a different definition of
neighborhood by restricting the number of replacements.} Classical
differential privacy requires the distributions of outcomes $0$,
$1$, and $2$ are similar on neighboring observations. For streaming
processing, observations are of indefinite lengths. Data analysis
algorithms necessarily stay in their internal states indefinitely
before outcomes are produced. Internal states however may reveal
private information. When data analysis algorithms are in internal
states, privacy may still be lost if an intrusion occurs. Classical
differential privacy is not very useful during continual observation.

In pan privacy, data analysis algorithms are required to respect
privacy even in their internal states~\cite{DNPR:10:DPCO,DNPRY:10:PPSA}.
